---
title: "Lab 01 - Hello R"
author: "Natalie Frye"
date: "01/30/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 columns. The variables included are the dataset, which indicates which dataset the data are from; x, which are the x-values; and y, which are the y-values.

### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=4.7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting of star dataset: 

```{r plot-star, fig.height=4.2, fig.width=4.5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation of x and y for star dataset:

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

It's quite similar to the correlation for the dino dataset.

### Exercise 4

Plot of the circle dataset: 

```{r fig.height=3, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Correlation of x and y in the circle dataset: 

```{r}
dino_data %>%
  summarize(r = cor(x, y))
```

Also a very similar correlation.

### Exercise 5

```{r fig.height=5, fig.width=5}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")
  
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
